MaBoSS for HPC environments: Implementations of the continuous time Boolean model simulator for large CPU clusters and GPU accelerators

### 2024-04-29 Article.tex
Added subparts for MaBoSS and CPU implementation, to write

Interactions in the model are described as transitions between two states. A single state can have multiple transitions to other states with assigned transition probabilities. In turn, a Boolean network is represented as a directed weighted graph $G = (\mathcal{S}, \rho)$, where $\rho: \mathcal{S} \times \mathcal{S} \rightarrow [0, \infty)$ is a transition function generating \emph{transition rates}. For convenience, it holds that:
\[ \rho(S, S') = 0 \iff \text{there is no transition from}\ S\ \text{to}\ S' \]
MaBoSS simulates the \emph{asynchronous update strategy}, where at most a single node changes its value in each transition --- consequently, a state $S$ can have at most $n$ possible transitions.

@@

>>>>

Interactions in the model are described as transitions between two states. A single state can have multiple transitions to other states with assigned transition probabilities. In turn, a Boolean network is represented as a directed weighted graph $G = (\mathcal{S}, \rho)$, where $\rho: \mathcal{S} \times \mathcal{S} \rightarrow [0, \infty)$ is a transition function generating \emph{transition rates}. For convenience, it holds that:
\[ \rho(S, S') = 0 \iff \text{there is no transition from}\ S\ \text{to}\ S' \]

\subsection{MaBoSS: Markovian Boolean Stochastic Simulator}
MaBoSS simulates the \emph{asynchronous update strategy}, where at most a single node changes its value in each transition --- consequently, a state $S$ can have at most $n$ possible transitions.

@@

\subsubsection{MaBoSS CPU Implementation}
MaBoSS is multi-core...
